%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Nitya Patel} \\ \vspace{1pt}
    \small +91-9131174431 $|$
    \href{mailto:nityapatel19@gmail.com}{\underline{nityapatel19@gmail.com}} $|$
    \href{https://linkedin.com/in/nityapatel19}{\underline{linkedin.com/in/nityapatel19}} $|$
    \href{https://github.com/nityapatel19}{\underline{github.com/nityapatel19}}
\end{center}


%-----------SUMMARY-----------
\section{Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     Backend software engineer with 2+ years of professional experience building distributed, event-driven systems and platform tooling in Python. Track record of owning systems end-to-end --- from design to production --- across high-volume trading infrastructure, applied ML, and API-driven applications.
    }}
 \end{itemize}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {IIIT Vadodara}{Gandhinagar, Gujarat}
      {B.Tech in Computer Science $|$ GPA: 8.61/10.0}{2020 -- 2024}
    \resumeSubheading
      {Shri Agrasen Vidyalaya}{Indore, MP}
      {Higher Secondary Certificate $|$ Score: 84.6\%}{2019}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Graviton Research Capital}{Gandhinagar / Gurugram}
      {Software Developer -- Tech Tools}{June 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Develop and maintain daily automations and exchange-specific workflows across 4 exchanges, ensuring reliable execution with consistent uptime.}
        \resumeItem{Build and own the \texttt{config\_converter} module, enabling zero-manual-intervention runs at 1000s of executions daily.}
        \resumeItem{Design a usage-based borrow allocation algorithm used across $\sim$30 strategies.}
        \resumeItem{Create internal tooling to eliminate repetitive tasks and improve team productivity.}
      \resumeItemListEnd

    \resumeSubheading
      {VizExperts}{Gurugram}
      {Software Development Intern}{January 2024 -- May 2024}
      \resumeItemListStart
        \resumeItem{Designed and built an AI-based live drift correction module from scratch using Python, OpenCV, and PyTorch, targeting iPad AR workflows without multi-camera hardware support.}
        \resumeItem{Achieved a $\sim$10--15$\times$ reduction in drift accumulation rate compared to baseline.}
        \resumeItem{Assisted with bug resolution in an AR/VR application built on Unreal Engine using C++ and Blueprint scripting.}
      \resumeItemListEnd

    \resumeSubheading
      {MathWorks}{Bangalore}
      {EDG Intern}{May 2023 -- July 2023}
      \resumeItemListStart
        \resumeItem{Added support for FMU 3.0 in the FMU Import Block component in Simulink.}
      \resumeItemListEnd

    \resumeSubheading
      {iHub-Data, IIIT Hyderabad}{Hyderabad}
      {Machine Learning Intern}{May 2022 -- July 2022}
      \resumeItemListStart
        \resumeItem{Contributed to a Dataset Foundation project to create a platform for ML/AI researchers.}
        \resumeItem{Collaborated with a team of 10 to design the project architecture and establish an efficient delivery pipeline.}
        \resumeItem{Engineered a high-throughput, multithreaded download manager using Python's \texttt{threading} module for concurrent dataset retrieval up to 100 GBs.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Algorithmic Trading Framework} $|$ \emph{Python, asyncio, REST APIs, Parquet}}{}
          \resumeItemListStart
            \resumeItem{Architected an event-driven trading infrastructure with a central EventBus --- fully decoupled components enable new exchanges or strategies as single-file additions without touching existing code.}
            \resumeItem{Implemented a live CoinDCX exchange adapter consuming REST APIs for OHLCV candle streaming, with a BaseExchange interface enabling multi-exchange support without architectural changes.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Ornithological Sound Identifier} $|$ \emph{Python, PyTorch}}{}
          \resumeItemListStart
            \resumeItem{Implemented a multilayered neural network that identifies birds from soundscapes.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Todoist Command Line Utility} $|$ \emph{Python}}{}
          \resumeItemListStart
            \resumeItem{Developed a command line utility for Todoist using the Todoist REST API.}
            \resumeItem{Handled API authentication, paginated resource fetching, and local state caching for a responsive offline-tolerant CLI experience.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C, C++, Java, JavaScript, Matlab, SQL, Bash} \\
     \textbf{Tools \& Frameworks}{: Git, Django, ReactJS, REST APIs, \LaTeX, Firebase, PyTorch} \\
     \textbf{Operating Systems}{: Windows, Linux}
    }}
 \end{itemize}


%-----------ACHIEVEMENTS-----------
\section{Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Giftabled Hackathon}{: 2nd rank among 100 participants --- created a facial recognition app embedded on an attachable pin, focused on helping visually impaired people.} \\
     \textbf{CTF}{: 3rd rank among 100 participants --- Capture the Flag; solved sequential puzzles involving cryptography, computer networks, web technology, and maths.} \\
     \textbf{Tech Hunt}{: 1st rank among 150 participants --- non-sequential puzzle competition; highest number of puzzles solved wins.}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
